% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
\usepackage{hyperref}
\usepackage{enumitem}
\hypersetup{pdfstartview={FitH},colorlinks=false,pdfborder={0 0 0},}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Yixin Luo} } % put text in header (right side)
%\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page


\begin{document}
\thispagestyle{plain} % this page has no header  
\name{Yixin Luo\\[12pt]}% the \\[12pt] adds a blank line after name

\pagenumbering{arabic}

\address{{\bf Contact} \\
{\em Cell phone:} (734) 546-7629 \\
{\em Email:} \href{mailto:yixinluo@cs.cmu.edu}{yixinluo@cs.cmu.edu} \\
{\em Webpage:} \href{http://www.yixinluo.com}{http://www.yixinluo.com} \\
}

\address{}

%\address{{\bf Office Address} \\ CIC 4\textsuperscript{th} Floor \\
%Carnegie Mellon University \\   Pittsburgh, PA 15213 }

%\address{{\bf Home Address} \\ 2 Bayard Rd, Apartment 55 \\ Pittsburgh, PA 15213 \\ (734) 546-7629 }


\begin{resume}

%==========================
%=== Research Statement ===
%==========================

\section{\centerline{OBJECTIVE}}
\vspace{8pt}
I am seeking a full-time research or engineering position in the industry where
I can use my expertise in storage systems and architectures to grow the company.


%==========================
%=== Research Statement ===
%==========================

% \section{\centerline{RESEARCH STATEMENT}} 
% \vspace{8pt}
% My research interest is in designing energy efficient, high performance and
% reliable computer architectures and systems in general. I am interested in
% problems related to datacenter infrastructure management, memory and storage
% systems, reliable and dependable computing, etc.


%=================
%=== Education ===
%=================

%\vspace{0.2in}
\section{\centerline{EDUCATION}} 
\vspace{8pt} 
{\bf Carnegie Mellon University}, Pittsburgh, PA \hspace{0.2in}
    \hfill September 2012 to December 2017 (Expected) \\
{\sl PhD candidate}, Computer Science Department \\
{\sl Relevant Courses}: Database Systems, Operating Systems and Distributed Systems,
Deep Reinforcement Learning, Machine Learning, Computer Architecture, Optimizing
Compilers, Computer Networks \\
\vspace{-6mm}

{\bf University of Michigan}, Ann Arbor, MI \hspace{0.2in}
    \hfill May 2012 \\
{\sl Bachelor of Science}, Computer Engineering \\
\vspace{-6mm}
 
{\bf Shanghai Jiao Tong University}, Shanghai, China
    \hfill August 2012 \\
{\sl Bachelor of Science}, Electrical Engineering


%==================
%=== Experience ===
%==================

\vspace{0.2in} 
\section{\centerline{EXPERIENCE}} 
\vspace{8pt}
{\bf Seagate Technology}, Lakeview, CA \hfill May to October 2016 \\
{\sl Engineering intern}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Developed new experimental characterization software to collect and analyze NAND flash errors and threshold voltage distribution.
  \item Applied data mining and modeling techniques to the collected raw NAND data for understanding flash error behavior.
  \item Designed new flash management policies to improve performance and reliability.
  \item Modified SSD controller firmware to assist raw NAND data collection.
\end{itemize}
{\bf Seagate Technology}, Lakeview, CA \hfill May to August 2015 \\
{\sl Engineering intern}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Constructed and analyzed model of NAND flash memory errors and threshold voltage distribution.
  \item Applied statistical modeling techniques to the collected raw NAND data for understanding flash error behavior.
  \item Designed new flash management policies to improve performance and reliability.
\end{itemize}
{\bf Microsoft Research}, Redmond, WA \hfill May to August 2013 \\
{\sl Research intern in Sensing and Energy Research Group (SERG)}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Characterized memory error vulnerability of data-intensive applications that runs in datacenters.
  \item Explored cost-efficient ways of tolerating memory errors in both software and hardware.
\end{itemize}
\vspace{-6pt}

\newpage
%====================
%=== Publications ===
%====================

\vspace{0.2in} 
\section{\centerline{PUBLICATIONS}}
\vspace{15pt}
\begin{itemize}[leftmargin=4mm]

  \item Yu Cai, Saugata Ghose, Erich F. Haratsch, \underline{Yixin Luo}, and Onur Mutlu,
        \href{https://arxiv.org/pdf/1706.08642}{\em ``Error Characterization, Mitigation, and Recovery in Flash Memory Based Solid-State Drives''},
        to appear in Proceedings of the IEEE, September 2017.
  \item Yu Cai, Saugata Ghose, \underline{Yixin Luo}, Ken Mai, Onur Mutlu, and Erich F. Haratsch,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/two-step-programming-vulnerability_hpca17.pdf}{\em ``Vulnerabilities in MLC NAND Flash Memory Programming: Experimental Analysis, Exploits, and Mitigation Techniques''},
        Proceedings of the 23rd International Symposium on High-Performance Computer Architecture (HPCA), February 2017.
  \item Aya Fukami, Saugata Ghose, \underline{Yixin Luo}, Yu Cai, and Onur Mutlu,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/chip-off-forensic_dfrws17.pdf}{\em ``Improving the Reliability of Chip-Off Forensic Analysis of NAND Flash Memory Devices''},
        Proceedings of the Digital Forensics Research Conference Europe (DFRWS EU), March 2017. {\bf (Best Paper Award)}
  \item \underline{Yixin Luo}, Saugata Ghose, Yu Cai, Erich F. Haratsch, and Onur Mutlu,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/online-flash-channel-modeling_jsac16.pdf}{\em ``Enabling Accurate and Practical Online Flash Channel Modeling for Modern MLC NAND Flash Memory''},
        IEEE Journal on Selected Areas in Communications (JSAC), September 2016.
  \item \underline{Yixin Luo}, Yu Cai, Saugata Ghose, Jongmoo Choi, and Onur Mutlu,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/write-hotness-aware-retention-management_msst15.pdf}{\em ``WARM: Improving NAND Flash Memory Lifetime with Write-hotness Aware Retention Management''},
        Proceedings of the 31st International Conference of Massive Storage Systems and Technologies (MSST), June 2015.
  \item Yu Cai, \underline{Yixin Luo}, Saugata Ghose, Erich F. Haratsch, Ken Mai, and Onur Mutlu,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/read-disturb-errors_dsn15.pdf}{\em ``Read Disturb Errors in MLC NAND Flash Memory: Characterization, Mitigation and Recovery''},
        Proceedings of the 45th International Conference on Dependable Systems and Networks (DSN), June 2015.
  \item Yu Cai, \underline{Yixin Luo}, Erich Haratsch, Ken Mai, Onur Mutlu,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/flash-memory-data-retention_hpca15.pdf}{\em ``Data Retention in MLC NAND Flash Memory: Characterization, Optimization and Recovery''}, 
        Proceedings of the 21st International Symposium on High-Performance Computer Architecture (HPCA), February 2015. {\bf (Best Paper Runner Up Award)}
  \item \underline{Yixin Luo}, Sriram Govindan, Bikash Sharma, Mark Santaniello, Justin Meza, Aman Kansal, Jie Liu, Badriddine Khessib, Kushagra Vaid, and Onur Mutlu, 
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/heterogeneous-reliability-memory_dsn14.pdf}{\em ``Characterizing Application Memory Error Vulnerability to Optimize Data Center Cost via Heterogeneous-Reliability Memory''},
        Proceedings of the 44th International Conference on Dependable Systems and Networks (DSN), June 2014.
  \item Vivek Seshadri, Yoongu Kim, Chris Fallin, Donghyuk Lee, Rachata Ausavarungnirun, Gennady Pekhimenko, \underline{Yixin Luo}, Onur Mutlu, Michael A. Kozuch, Phillip B. Gibbons, and Todd C. Mowry,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/rowclone_micro13.pdf}{\em ``RowClone: Fast and Energy-Efficient In-DRAM Bulk Data Copy and Initialization''},
        Proceedings of the 46th International Symposium on Microarchitecture (MICRO), December 2013.
  \item Justin Meza, \underline{Yixin Luo}, Samira Khan, Jishen Zhao, Yuan Xie, and Onur Mutlu,
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/persistent-memory-management_weed13.pdf}{\em ``A Case for Efficient Hardware-Software Cooperative Management of Storage and Memory''},
        Proceedings of the 5th Workshop on Energy-Efficient Design (WEED), Tel-Aviv, Israel, June 2013.
  \item Joseph L. Greathouse, Hongyi Xin, \underline{Yixin Luo}, Todd M. Austin.
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/unlimited-watchpoints_asplos12.pdf}{\em ``A Case for Unlimited Watchpoints''},
        Proceedings of the 17th International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), March 2012.
  \item Arun Raghavan, \underline{Yixin Luo}, Anuj Chandawalla, Marios C. Papaefthymiou, Kevin P. Pipe, Thomas F. Wenisch, Milo M. K. Martin.
        \href{http://www.cs.cmu.edu/~yixinluo/index_files/computational-sprinting_hpca12.pdf}{\em ``Computational Sprinting''},
        Proceedings of the 18th International Symposium on High-Performance Computer Architecture (HPCA), February 2012. {\bf (Best Paper Award)} \\
        {\em One of the 11 computer architecture papers of 2012 selected as Top Picks by IEEE Micro.}
\end{itemize}

%=======================
%=== Technical Talks ===
%=======================

\vspace{0.2in} 
\section{\centerline{TECHNICAL TALKS}}
\vspace{15pt}
\begin{itemize}[leftmargin=4mm]

  \item \href{http://www.cs.cmu.edu/~yixinluo/index_files/online-flash-channel-modeling_fms16-talk.pptx}{\em ``Online Flash Channel Modeling and Its Applications''},
        Flash Memory Summit (FMS), 2016.
  \item \href{http://www.cs.cmu.edu/~yixinluo/index_files/data-retention_fms15.pptx}{\em ``Data Retention in MLC NAND Flash Memory''},
        Flash Memory Summit (FMS), 2015.
  \item \href{http://www.cs.cmu.edu/~yixinluo/index_files/write-hotness-aware-retention-management_msst15-talk.pptx}{\em ``WARM: Improving NAND Flash Memory Lifetime with Write-hotness Aware Retention Management''},
        International Conference on Massive Storage Systems and Technology (MSST), 2015.
  \item \href{http://www.cs.cmu.edu/~yixinluo/index_files/read-disturb-errors_dsn15-talk.pptx}{\em ``Read Disturb Errors in MLC NAND Flash Memory''},
        International Conference on Dependable Systems and Networks (DSN), 2015.
  \item \href{http://www.cs.cmu.edu/~yixinluo/index_files/flash-memory-data-retention_hpca15-talk.pptx}{\em ``Data Retention in MLC NAND Flash Memory''},
        IEEE Symposium on High Performance Computer Architecture (HPCA), 2015. {\bf (Best Paper Session)}
  \item \href{http://www.cs.cmu.edu/~yixinluo/index_files/heterogeneous-reliability-memory_dsn14-talk.pptx}{\em ``Optimizing Datacenter Cost via Heterogeneous Reliability Memory''},
        International Conference on Dependable Systems and Networks (DSN), 2014.
        
\end{itemize}

%%==============================
%%=== Paper under submission ===
%%==============================
%
%\vspace{0.2in} 
%\section{\centerline{PAPER UNDER SUBMISSION}}
%\vspace{15pt}
%\begin{itemize}[leftmargin=4mm]
%\end{itemize}

%================
%=== Projects ===
%================

\vspace{0.2in} 
\section{\centerline{PROJECTS}} 
\vspace{8pt}
{\bf Research Projects} \vspace{2pt} \\
{\bf \em Architectural Techniques for Improving NAND Flash Memory Reliability}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Developed new experimental characterization software to record and analyze NAND flash memory errors and threshold voltage distribution.
  \item Applied various data mining and modeling techniques to study raw NAND data.
  \item Designed new flash management policies to improve performance and reliability.
\end{itemize}
{\bf \em Heterogeneous Reliability Memory for Data Centers}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Developed a memory error injection and monitoring framework for data-intensive applications.
  \item Performed a case study of application memory error tolerance on three data-intensive applications.
  \item Explored the design space of heterogeneous-reliability memory systems.
\end{itemize}
{\bf \em Single-Level Storage}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Analyzed and simulated the performance, energy, and scalability improvement of a single-level storage system compared to a traditional two-level storage system.
\end{itemize}
{\bf \em Computational Sprinting}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Established a SPICE power model for power gating many-core processors.
  \item Developed a circuit-level method to reduce performance overhead for power gating.
  \item Performed SPICE circuit simulations to show the performance benefit of Computational Sprinting.
\end{itemize}
{\bf \em A Case for Unlimited Watchpoints}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Developed and simulated the performance benefits of applying the proposed hardware watchpoint support to a variety of software analyses.
\end{itemize}
{\bf Other Projects} \vspace{2pt} \\
% TODO: add projects here
{\bf \em CPU Architecture Design} {\em (Bachelor Major Design Project)}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Designed and implemented an out-of-order processor in SystemVerilog.
\end{itemize}
{\bf \em CPU Layout Design} {\em (Bachelor Major Design Project)}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Designed the circuit layout for an in-order processor and a 3-transistor
    eDRAM cache.
\end{itemize}
\vspace{-6pt}

%===========================
%=== Teaching experience ===
%===========================

\vspace{0.2in}
\section{\centerline{TEACHING EXPERIENCE}}
\vspace{8pt}
{\bf Teaching Assistant}, Carnegie Mellon University \hfill Fall 2014 \\
{\sl Research in Parallel Computer Architecture (18-742)}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Responsibilities include holding office hours, shepherding student
    projects.
\end{itemize}
{\bf Teaching Assistant}, Carnegie Mellon University \hfill Spring 2014 \\
{\sl Parallel Computer Architecture and Programming (15-418/15-618)}
\begin{itemize} \itemsep -2pt % reduce space between items
  \item Responsibilities include holding office hours, shepherding projects,
    preparing and grading homeworks.
\end{itemize}
\vspace{-6pt}

%========================
%=== Technical skills ===
%========================

\vspace{0.2in} 
\section{\centerline{TECHNICAL SKILLS}}
\vspace{15pt}
\begin{itemize}[leftmargin=4mm] \itemsep -2pt % reduce space between items
  \item {\em Lanuages:} {\tt C/C++}, {\tt Perl/Python}, {\tt Linux Shell}, \LaTeX, {\tt Verilog}, {\tt Windows Batch script}
  \item {\em Tools:} {\tt Matlab}, {\tt Intel Pin}, {\tt HSPICE}, {\tt Cadence tools}
  \item {\em Simulators:} {\tt gem5}, {\tt Multi2Sim}
  \item {\em Others:} {\tt Hadoop}, {\tt MySQL}
\end{itemize}


%\newpage


 
\end{resume} 
\end{document}


